---
title       : coursera data product project
subtitle    : Motor Trend Car Road Tests
author      : unijoy
job         : enginner
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data Description

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

--- .class #id 

## Model 

Just keep things simple ,we choice :

 1. "Number of cylinders"
 2. "Gross horsepower"
 3. "Weight(lb/1000)" 
 
as our predictors

and we will predict Miles/(US) gallon

---
## Prediction
The prediction function

```{r,echo=TRUE}

mypredciton <- function(cyl,hp,wt){
    if(cyl != 0 & hp != 0 & wt !=0 ){
        modelFit <- lm(mpg ~ cyl + hp + wt,data=mtcars)
        df<- data.frame(cyl=cyl,hp=hp,wt=wt)
        predict(modelFit,newdata = df)    
    }
    
}

```


---
## Result
Using test data for our function to predict Miles/(US) gallon:

```{r}
mypredciton(6,110,2.62)
```




